### 2019-03-22 dantzig_selector/report/4_simulation.tex
Set & correct simulation variables

\startsection [title={Transformation of the Problem}]

\startsubsection [title={Representation by Real Matrices}]

@@

\Result
{Definition}
{
For \m {x \in \Mb {V} \SB {M}}, we say that \m {\Mc {R} \SB {x}} is the real representation of \m {x}, defined by
%
\Disp {
\NC \Mc {R} \SB {x} \in \NC \Mb {V} \SB {2M} \NR[+]
\NC \Mc {R} \SB {x} \DB {m} =
\NC \startcases
\NC \Mf {Re} \SB {\Mc {R} \SB {x} \DB {m'}}, \MC m =2m' \NR
\NC \Mf {Im} \SB {\Mc {R} \SB {x} \DB {m'}}, \MC m =2m'+1 \NR
\stopcases \NR[+]
\NC m' = \NC  1, \dots, M \NR
}
%
}

@@

\Result
{Definition}
{
For \m {A \in \Mb {M}_{\Mb {C}} \SB {M_1, M_2}}, we say that \m {\Mc {R} \SB {A}} is the real representation of \m {A}, defined by
%
\Disp {
\NC A \in \NC \Mb {V}_{\Mb {R}} \SB {2M_1, 2M_2} \NR[+]
\NC A \DB {m_1,m_2} =
\NC \startcases
\NC \Mf {Re} \SB {A \SB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2'-1) \NR
\NC \Mf {Im} \SB {A \SB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2'-1) \NR
\NC -\Mf {Im} \SB {A \SB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2') \NR
\NC \Mf {Re} \SB {A \SB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
\stopcases \NR[+]
\NC m_1' = \NC 1, \dots, m_1 \NR[+]
\NC m_2' = \NC 1, \dots, m_2 \NR
}
%
}

@@

%
\Disp {
\NC \V {\T {y}}
= \NC \Mc {R} \SB {y}
\in \Mb {V} \SB {2N_y} \NR[+]
\NC \V {\T {g}}
= \NC \Mc {R} \SB {g}
\in \Mb {V} \SB {2N_h} \NR[+]
\NC \M {\T {P}}
= \NC \Mc {R} \SB {\M {P}}
\in \Mb {M}_{\Mb {C}} \SB {2N_y, 2N_h} \NR[+]
\NC \V {\T {z}}
= \NC \Mc {R} \SB {\V {z}} \in \Mb {V} \SB {2N_y} \NR[+]
}
%
such that, by construction,
%
\Disp {
\NC \V {\T {y}} = \NC \M {\T {P}} \V {\T {g}} +\V {\T {z}}
}
%

@@

%
\Disp {
\NC {\T {\M {u}}}_{n_y}^{(y)} \in \NC \Mb {M}_{\Mb {R}} \SB {2N_y, 2N_y} \NR
\NC {\T {\M {u}}}_{n_y}^{(y)} \DB {m_y}
= \NC
\startcases
1, \quad \MC m_y =2n_y \NR
1, \quad \MC m_y =2n_y +1 \NR
0, \quad \NC {\rm otherwise}
\stopcases \NR[+]
\NC {\T {\M {U}}}_{n_h}^{(h)} \in \NC \Mb {M}_{\Mb {R}} \SB {2N_h, 2N_h} \NR
\NC {\T {\M {U}}}_{n_h}^{(h)} \DB {m_h, m_h'}
= \NC
\startcases
1, \quad \MC m_h =2n_h,\; m_h' =2n_h \NR
1, \quad \MC m_h =2n_h +1,\; m_h' =2n_h \NR
1, \quad \MC m_h =2n_h,\; m_h' =2n_h +1\NR
1, \quad \MC m_h =2n_h +1,\; m_h' =2n_h +1 \NR
0, \quad \NC {\rm otherwise}
\stopcases \NR[+]
\NC n_y, m_y = \NC 1, \dots, N_y \NR
\NC n_h, m_h, m_h' = \NC 1, \dots, N_h \NR
}
%

If we introduce vector \m {\V {m} \in \Mb {M}_{\Mb {V}} \SB {N_y}} to denote the entrywise complex modulus, we see that the convex optimization now take the form
\Disp {
\NC \T {\V {g}}
= \NC \startcases
\NC \Min {\T {\V {g}}, \V {m}} \quad
\MC \IP { \V {1}, \V {m} } \NR
\NC \Mr {subject} \; \Mr {to} \quad
\MC \VNm { \M {U}_{n_h}^{(h)} \T {\V {g}} }_2
\leq \IP { \V {u}_{n_h}, \V {m} } \NR
\NC \MC \VNm { \M {U}_{n_y}^{(y)} \T {\M {P}}^\Adj \RB { \T {\M {P}} \T {\V {g}} -\T {\V {y}} } }_2
\leq \gamma \NR
\stopcases \NR
}
where \m {\V {1} \in \Mb {M}_{\Mb {V}} \SB {N_y}} is the all-1 vector.

\stopsubsection

\startsubsection [title={Second Order Cone Problem}]

We shall see furthermore that the program can be cast into an SOCP.
To make the point clearer, we rewrite Program () into a stricter, extended block matrix form
\Result
{Algorithm}
{
\startitemize[n]
\item Input \m{\M {P} \in \Mb {M}_{\Mb {C}} \SB {N_y, N_h}}, \m{\V {y} \in \Mb {V}_{\Mb {C}} \SB {N_h}}, \m{\gamma \geq 0}.
\item Input \m{\hat {\M {P}} \in \Mb {M}_{\Mb {C}} \SB {N_y, N_h}}, \m{\hat {\V {y}} \in \Mb {V}_{\Mb {C}} \SB {N_h}}.
\item Calculate
\item Output \m {\hat {\M {H}}}.
\stopitemize
}

\startsection [title={Primal-Dual Interior Point Algorithm}]

It remains to convert primal-dual interior point algorithm to make the SOCP easier to calculate.
Of course it is not the only way to do this.
We mention, again, Boyd and Vandenberghe (2004), {\it Convex Optimization} chap.11 as a standard reference, and ``\m {\ell_1}-MAGIC'' (Cand\`es and J Romberg 2005) for discussion of application to DS.

To clarify notation and for complentess of exposition, we derive the dual problem here.
Start with the Lagrangian \m {\Mc {L}}, where we note we have to introduce one auxiliary vector and one auxiliary scalar for each \m {\ell_2}-norm constraint.

%
\Disp {
\NC \NC \Mc {L} \SB {\V {m}, \T {\V {g}}, \V {\mu}^{(h)}, \V {\mu}^{(y)}, \lambda^{(h)}, \lambda^{(y)}} \NR[+]
\NC = \NC \IP {\V {1}, \V {m}}
+\sum_{n_h} \SB {\IP {\V {\mu}^{(h)}, \M {I}_{n_h}^{(h)} \T {\M {g}}} -\lambda^{(h)} \IP {\V {y}_{n_h}, \V {m}}} \NR[+]
\NC \quad \NC  +\sum_{n_y} \SB { \IP { \V {\mu}^{(h)}, \M {I}_{n_y}^{(y)} \T {\M {P}}^\Adj \RB { \T {\M {P}} \T {\V {g}} -\T {\V {y}} } } -\lambda^{(h)} \gamma} \NR[+]
}
%

@@

On the other hand, DS goes not without criticism for large complexity of it (Friedlander and Saunders 2007).
Indeed it is clear, even from the primal-dual implementation above, that DS requires memory for large dimensional vector, but OMP does not.

@@

>>>>

\startsection [title={Representation by Real Matrices}]

@@

\Result
{Definition}
{
For \m {x \in \Mb {V} \SB {M}}, we say that \m {\Mc {R} \SB {x}} is the real representation of \m {x}, defined by
%
\Disp {
\NC \Mc {R} \SB {x} \in \NC \Mb {V} \SB {2M} \NR[+]
\NC \Mc {R} \SB {x} \DB {m} =
\NC \startcases
\NC \Mf {Re} \SB {x \DB {m'}}, \MC m =2m' \NR
\NC \Mf {Im} \SB {x \DB {m'}}, \MC m =2m'+1 \NR
\stopcases \NR[+]
\NC m' \NC =  1, \dots, M \NR
}
%
}

@@

\Result
{Definition}
{
For \m {A \in \Mb {M}_{\Mb {C}} \SB {M_1, M_2}}, we say that \m {\Mc {R} \SB {A}} is the real representation of \m {A}, defined by
%
\Disp {
\NC \Mc {R} \SB {A} \in \NC \Mb {M}_{\Mb {R}} \SB {2M_1, 2M_2} \NR[+]
\NC \Mc {R} \SB {A} \DB {m_1,m_2} =
\NC \startcases
\NC \Mf {Re} \SB {A \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2'-1) \NR
\NC \Mf {Im} \SB {A \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2'-1) \NR
\NC -\Mf {Im} \SB {A \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2') \NR
\NC \Mf {Re} \SB {A \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
\stopcases \NR[+]
\NC m_1' \NC = 1, \dots, M_1 \NR
\NC m_2' \NC = 1, \dots, M_2 \NR
}
%
}

@@

%
\Disp {
\NC \T {\V {y}}
\NC = \Mc {R} \SB {\V {y}}
\in \Mb {V}_{\Mb {R}} \SB {2N_y} \NR[+]
\NC \T {\V {g}}
\NC = \Mc {R} \SB {\V {g}}
\in \Mb {V}_{\Mb {R}} \SB {2N_h} \NR[+]
\NC \T {\M {P}}
\NC = \Mc {R} \SB {\M {P}}
\in \Mb {M}_{\Mb {R}} \SB {2N_y, 2N_h} \NR[+]
\NC \T {\V {z}}
\NC = \Mc {R} \SB {\V {z}} \in \Mb {V}_{\Mb {R}} \SB {2N_y} \NR[+]
}
%
such that, by construction,
%
\Disp {
\NC \V {\T {y}} \NC = \M {\T {P}} \V {\T {g}} +\V {\T {z}}
}
%

@@

%
\Disp {
\NC {\V {u}}_{n_h}^{(h)} \in \NC \Mb {V}_{\Mb {R}} \SB {N_h} \NR[+]
\NC {\V {u}}_{n_h}^{(h)} \DB {n_h'}
\NC =
\startcases
1, \quad \MC n_h' =n_h \NR
0, \quad \NC {\rm otherwise}
\stopcases \NR[+]
\NC {\T {\M {U}}}_{n_h}^{(h)} \in \NC \Mb {M}_{\Mb {R}} \SB {2N_h, 2N_h} \NR[+]
\NC {\T {\M {U}}}_{n_h}^{(h)} \DB {n_h', n_h''}
\NC =
\startcases
1, \quad \MC n_h' =2n_h -1,\; n_h'' =2n_h -1 \NR
1, \quad \MC n_h' =2n_h,\; n_h'' =2n_h -1 \NR
1, \quad \MC n_h' =2n_h -1,\; n_h'' =2n_h \NR
1, \quad \MC n_h' =2n_h,\; n_h'' =2n_h \NR
0, \quad \NC {\rm otherwise}
\stopcases \NR[+]
\NC n_h, n_h', n_h'' \NC = 1, \dots, N_h \NR
}
Moreover, denote \m {\V {1}} to be the all-\m{1} vector for short, and \m {\V {0}} the all-\m{0} vector, whose dimension will be specified from context.
Now, if we introduce vector \m{\V{m}}

\Disp{
\NC \V {m} \NC \in \Mb {V}_{\Mb {R}} \SB {N_h} \NR[+]
\NC \V{m} \DB{n_h}
\NC =\Nm{\V{g} \DB{n_h}} \NR[+]
\NC n_h, n_h', n_h'' \NC = 1, \dots, N_h \NR
}

to denote the entrywise complex modulus of \m{\V {g}}, we see that the convex optimization now take the form
\Disp {
\NC \Hat {\T {\V {g}}}
\NC = \startcases
\NC \Min {\T {\V {g}}', \V {m}} \quad
\MC \IP { \V {1}, \V {m} } \NR
\NC \Mr {subject} \; \Mr {to} \quad
\MC \VNm { \T {\M {U}}_{n_h}^{(h)} \T {\V {g}}' }_2
\leq \IP { \V {u}_{n_h}, \V {m} } \NR
\NC \MC \VNm { \T {\M {U}}_{n_h}^{(h)} \T {\M {P}}^\Adj \RB { \T {\M {P}} \T {\V {g}}' -\T {\V {y}} } }_2
\leq \g \NR
\stopcases \NR[+]
\NC n_h \NC = 1, \dots, N_h \NR
}

\stopsection

\startsection [title={Second Order Cone Programming}]

We shall see furthermore that the program can be cast into an SOCP.
To make the point clearer, we rewrite Program () into a stricter, extended block matrix form, by defining auxiliary variables with dimension

\Disp{
\NC \V{t}_i
\NC \in \Mb {V}_{\Mb {R}} \SB {2N_y +N_h} \NR[+]
\NC \V{x}_i
\NC \in \Mb {V}_{\Mb {R}} \SB {2N_y +N_h} \NR[+]
\NC \M{A}_i
\NC \in \Mb {M}_{\Mb {R}} \SB {2N_h, 2N_y +N_h} \NR[+]
\NC \V{b}_i
\NC \in \Mb {V}_{\Mb {R}} \SB {2N_y +N_h} \NR[+]
\NC \V{c}_i
\NC \in \Mb {V}_{\Mb {R}} \SB {2N_h} \NR[+]
\NC d_i
\NC \in \Mb {R} \NR[+]
}

defined below to be

\Disp{
\NC \V{t}
\NC =\startthematrix
\NC \V{0} \NR
\NC \V{1} \NR
\stopthematrix \NR[+]
\NC \V{x}'
\NC =\startthematrix
\NC \T {\V {g}}' \NR
\NC \V{m} \NR
\stopthematrix \NR[+]
}

with

\Disp{
\NC \M{A}_i
\NC =\startthematrix
\NC \T {\M {U}}_{n_h}^{(h)}, \NC \M{0} \NR
\stopthematrix \NR[+]
\NC \V{b}_i
\NC =\startthematrix
\NC \V{0} \NR
\NC \V{0} \NR
\stopthematrix \NR[+]
\NC \V{c}_i
\NC =\startthematrix
\NC \V{0} \NR
\NC \V {u}_{n_h} \NR
\stopthematrix \NR[+]
\NC d_i
\NC =0 \NR[+]
\NC i \NC =1, 2, \dots, N_h \NR
}

And

\Disp{
\NC \M{A}_i
\NC =\startthematrix
\NC \T {\M {U}}_{n_h}^{(h)} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M{0} \NR
\stopthematrix \NR[+]
\NC \V{b}_i
\NC =\startthematrix
\NC -\T {\M {U}}_{n_h}^{(h)} \T {\M {P}}^\Adj \T {\V {y}} \NR
\NC \V{0} \NR
\stopthematrix \NR[+]
\NC \V{c}_i
\NC =\startthematrix
\NC \V{0} \NR
\NC \V{0} \NR
\stopthematrix \NR[+]
\NC d_i
\NC =\g \NR[+]
\NC i \NC =N_h +1, N_h +2, \dots, N_h +N_y \NR
}

The step that we convert \m {\Hat {\V {g}}} back is same as Algorithm () is same as before, but this is listed for sake of completeness.

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m{\M {P} \in \Mb {M}_{\Mb {C}} \SB {N_y, N_h}}, \m{\V {y} \in \Mb {V}_{\Mb {C}} \SB {N_y}}, \m{\g \geq 0}.
\item Define \m{\V{t}, \V{x}, \M{A}_i, \V{b}_i, \V{c}_i, d_i} according to ().
\item Calculate
\Disp{
\NC \Hat {\V {x}}
\NC = \startcases
\NC \Min {\V {x}' \in \Mb {V}_{\Mb {C}} \SB {N_h}}
\MC \IP {\V {t}, \V {x}'} \NR[+]
\NC \Mr {subject} \; \Mr {to}
\quad  \MC \VNm {\M {A} _{i} \V {x}' +\V{b} _{i}} _2
\leq \IP {\V{c}_{i}, \V {x}'} +\V{d}_i \NR
\NC \MC i =1, 2, \dots, N_y +N_h \NR
\stopcases \NR[+]
}
\item Extract
\Disp{
\NC \Hat{\T{\V{g}}} =\NC \Hat{\V{x}} \DB {1 : 2N_h} \NR[+]
}
\item Convert 
\Disp{
\NC \Hat{\V{g}} =\NC \Mc{R} ^{-1} \SB {\Hat{\T{\V{g}}}} \NR[+]
}
\item Calculate
\Disp {
\NC \Hat {G} =\Mr {vec}^{-1} \SB {\Hat {g}} \NR[+]
}
\item Calculate
\Disp {
\NC \Hat {\M {H}} =\M {K} \Hat {\M {G}} \M {K}^\Adj \NR[+]
}
\item Output \m {\Hat {\M {H}}}.
\stopitemize
}

\stopsection

\startsection [title={Simulation}]

One can convert primal-dual interior point algorithm to make the SOCP easier to calculate.
We mention, again, Boyd and Vandenberghe (2004), {\it Convex Optimization} chap.\ 11 as a standard reference, and ``\m {\ell_1}-MAGIC'' (Cand\`es and J Romberg 2005) for discussion of SOCP applied to DS.

However, for brevity we use Python Library CVXPY to solve the SOCP.

\stopsection

@@

On the other hand, DS goes not without criticism for its large complexity (Friedlander and Saunders 2007).
Indeed it is clear, even from the primal-dual implementation above, that DS requires memory for large dimensional vector, but OMP does not.

@@

\stopsection
